Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-16 writing/embedded_meta_learning.tex
Sweeping poly

\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results}. \par 

@@

\section{Supplemental figures}
\begin{figure}[H]
\centering
\includegraphics[width=0.66\textwidth]{figures/continual/continual_learning_direct_comparison.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting with the guessed embedding substantially speeds-up the process compared to a randomly-initialized embedding. Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.}
\label{supp_poly_continual_results}
\end{figure}

>>>>

\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results}. Furthermore, it is able to do this in a sample-efficient manner, see supp. fig. \ref{supp_poly_sweep_results}. \par 

@@

\section{Supplemental figures}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/basic_results_sweeping.png}
\caption{The system is able to infer polynomials from only seeing a few data points (i.e. evaluations of the polynomial), despite the fact that during training it always saw 50. A minimum of 15 random points is needed to correctly infer polynomials without prior knowledge of the polynomial distribution, but the system is performing well below this value, and quite well above it, although it continues to refine its estimates slightly when given more data.}
\label{supp_poly_sweep_results}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/continual/continual_learning_direct_comparison.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting with the guessed embedding substantially speeds-up the process compared to a randomly-initialized embedding. Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network.}
\label{supp_poly_continual_results}
\end{figure}
